Phenomenological Robotics

### 2011-12-21 draft.tex
Wrote on the relation of the work to affordances.

>>>>

% 1.C. Relation to affordances.
% (Source: Thesis journal, pages 130 to 139, 16/03/2011).
% Note: the following two paragraphs only introduce affordances and a reason
% for using it in robotics. Citing Chemero (2003) might be needed too. Examples
% of affordance based robotics (from Rome's book) should be in section 3.

Gibson~\cite{gibson1979} defines the \emph{affordances} of the environment as

\begin{quotation}
  \dots what it \emph{offers} the animal, what it \emph{provides} or
  \emph{furnishes}, either for good or ill. \dots [S]omething that refers to
  both the environment and the animal \dots.
\end{quotation}

Rome, Hertzberg and Dorffner~\cite{rome2008}, in their preface to ``Towards
Affordance-Based Robot Control'', affirm that the concept of affordance has
rarely been used in robotics or artificial intelligence, despite the original
perspective it offers on coupling perception, action and reasoning.
